\documentclass[10pt]{article}
\usepackage[margin=1in,landscape]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{array}
\usepackage{ragged2e}
\newcolumntype{L}[1]{>{\RaggedRight\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\RaggedLeft\arraybackslash}p{#1}}
\renewcommand{\arraystretch}{1.05}
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}
\sloppy
\begin{document}
\begin{center}\LARGE\textbf{NBA Strategy Brief}\end{center}
\vspace{0.5em}
\section*{Strategy Brief}

\subsection*{Snapshot}
\begin{itemize}
\item snapshot\_id: \texttt{daily-20260212T230052Z}
\item modeled\_date\_et: \texttt{Thursday, Feb 12, 2026 (ET)}
\item generated\_at\_et: \texttt{2026-02-12 06:00:58 PM EST}
\item source\_data: \texttt{snapshot\_inputs}
\item scoring: \texttt{deterministic}
\item narrative: \texttt{llm}
\end{itemize}

\subsection*{What The Bet Is}

\begin{itemize}
\item Bet type: single-player props (over/under stat lines).
\item Not a game-winner (moneyline) strategy.
\item Injury and roster checks are used as action gates.
\item Tier A = 2+ book quotes for a line; Tier B = a single-book quote.
\end{itemize}

\subsection*{Executive Summary}

\begin{itemize}
\item Top-tier player prop opportunities across DAL@LAL and MIL@OKC; multiple GO plays with positive EVs and verified availability. Watch for listed model/data gaps and several NO-GO items tied to questionable injury status.
\item Eligible plays: \texttt{181} out of \texttt{190} candidate lines.
\item Tier-B mode: \texttt{enabled}. Candidate mix: Tier A \texttt{110}, Tier B \texttt{80}.
\item Gated-out lines hidden from this brief: \texttt{5}.
\item First-page table below shows the top \texttt{5} plays across all games.
\end{itemize}

\newpage

\subsection*{Analyst Take}

\begin{itemize}
\item mode: \texttt{llm\_web}
\end{itemize}

\subsubsection*{Read This First}

The model identifies several high-expected-value (EV) player prop 'GO' recommendations concentrated on the DAL@LAL game, notably LeBron James (two props), Austin Reaves, Marcus Smart, and Jake LaRavia. The deterministic model uses market-implied probabilities with manual adjustments for injuries and rostering, but it also lists explicit gaps: minutes/usage projections and correlation treatments follow deterministi...

\subsubsection*{News Signals}

\begin{itemize}
\item Refutes/Risks:
\item [S1] Recent reporting indicates Austin Reaves will miss at least a month with a calf injury, which directly challenges the reliability of any GO recommendation depending on his availability.
\item [S2] Multiple news reports and injury updates show Austin Reaves has been on the Lakers injury report and there is coverage of his return/status, highlighting uncertainty about his game availability.
\item [S3] News coverage documents Austin Reaves' injury situation and team updates, indicating evolving status that could invalidate model assumptions about his minutes/usage.
\end{itemize}

\subsubsection*{Bottom Line}

\begin{itemize}
\item \textbf{Best Bet:} \textbf{LeBron James OVER 40.5 points+rebounds+assists @ -106 (fanduel)}
\item \textbf{Lookup Line:} \texttt{DAL @ LAL} | \texttt{OVER 40.5 points+rebounds+assists} | \texttt{fanduel -106}
\end{itemize}
The model highlights attractive EV plays, mainly in DAL@LAL, but its deterministic handling of minutes/usage and correlation is a stated gap. More importantly, external news shows Austin Reaves has a significant calf injury with uncertain availability; that materially undermines any Reaves prop recommendation and raises caution for model outputs tied to roster/injury assumptions.

\subsubsection*{Source Index}

\begin{itemize}
\item [S1] Austin Reaves will miss at least a month with calf injury - NBA.com (www.nba.com)
\item [S2] Lakers' Austin Reaves off injury report for Thursday - CBS Sports (www.cbssports.com)
\item [S3] Lakers Austin Reaves injury coverage - The Washington Post (www.washingtonpost.com)
\item Deterministic model details are summarized in Snapshot/Action Plan.
\item Full source URLs are stored in \texttt{brief-analyst.json} for audit/debug use.
\end{itemize}

\newpage

\subsection*{Best Available Bet Right Now}

\begin{itemize}
\item \textbf{Decision:} \textbf{GO} (meets clean GO gates in this snapshot.)
\item \textbf{Bet:} \textbf{LeBron James OVER 40.5 points+rebounds+assists @ -106 (fanduel)}
\item \textbf{Lookup Line:} \texttt{DAL @ LAL} | \texttt{OVER 40.5 points+rebounds+assists} | \texttt{fanduel -106}
\item \textbf{Model Edge:} \texttt{+33.0\% est.}
\item why: Go: verified availability with tier A market depth and positive edge (EV 0.330).
\end{itemize}

\newpage

\subsection*{Action Plan (GO / LEAN / NO-GO)}

\subsubsection*{Top 5 Across All Games}

{\small
\setlength{\tabcolsep}{2pt}
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\begin{longtable}{|L{0.089\linewidth}|L{0.164\linewidth}|L{0.089\linewidth}|L{0.150\linewidth}|R{0.068\linewidth}|L{0.150\linewidth}|L{0.150\linewidth}|}
\hline
\textbf{Action} & \textbf{Game} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endfirsthead
\hline
\textbf{Action} & \textbf{Game} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
GO & DAL @ LAL & A & LeBron James OVER 40.5 points+rebounds+assists @ -106 (fanduel) & 68.4\% & Strong edge (+33.0\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.330). (tier=A; injury=available\_unlisted; roster=active) \\
\hline
GO & DAL @ LAL & A & Austin Reaves OVER 36.5 points+rebounds+assists @ -106 (fanduel) & 68.1\% & Strong edge (+32.4\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.324). (tier=A; injury=available\_unlisted; roster=active) \\
\hline
GO & DAL @ LAL & A & Marcus Smart OVER 18.5 points+rebounds+assists @ -102 (fanduel) & 66.0\% & Strong edge (+30.7\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.307). (tier=A; injury=available\_unlisted; roster=active) \\
\hline
GO & DAL @ LAL & B & Jake LaRavia OVER 16.5 points+rebounds+assists @ -102 (draftkings) & 65.8\% & Strong edge (+30.3\% est.), Higher stake & Go: verified availability with tier B market depth and positive edge (EV 0.303). (tier=B; injury=available\_unlisted; roster=active) \\
\hline
GO & DAL @ LAL & A & LeBron James OVER 8.5 assists @ +112 (fanduel) & 61.4\% & Strong edge (+30.1\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.301). (tier=A; injury=available\_unlisted; roster=active) \\
\hline
\end{longtable}
}




\newpage

\subsection*{Game Cards by Matchup}

\subsubsection*{MIL @ OKC}
\begin{itemize}
\item Tip (ET): \texttt{07:40 PM ET}
\item Listed plays: \texttt{5}
\end{itemize}

{\small
\setlength{\tabcolsep}{2pt}
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\begin{longtable}{|L{0.112\linewidth}|L{0.112\linewidth}|L{0.190\linewidth}|R{0.086\linewidth}|L{0.190\linewidth}|L{0.190\linewidth}|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endfirsthead
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
GO & A & Cason Wallace OVER 20.5 points+rebounds+assists @ -108 (fanduel) & 67.1\% & Strong edge (+29.2\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.292). \\
\hline
GO & A & Kevin Porter Jr. OVER 31.5 points+rebounds+assists @ -107 (draftkings) & 66.3\% & Strong edge (+28.4\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.284). \\
\hline
GO & A & Chet Holmgren OVER 30.5 points+rebounds+assists @ -108 (fanduel) & 66.2\% & Strong edge (+27.4\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.274). \\
\hline
GO & A & Jericho Sims OVER 5.5 points @ +100 (draftkings) & 63.6\% & Strong edge (+27.3\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.273). \\
\hline
GO & A & Aaron Wiggins OVER 24.5 points+rebounds+assists @ -111 (fanduel) & 66.9\% & Strong edge (+27.1\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.271). \\
\hline
\end{longtable}
}


\newpage

\subsubsection*{POR @ UTA}
\begin{itemize}
\item Tip (ET): \texttt{09:10 PM ET}
\item Listed plays: \texttt{1}
\end{itemize}

{\small
\setlength{\tabcolsep}{2pt}
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\begin{longtable}{|L{0.112\linewidth}|L{0.112\linewidth}|L{0.190\linewidth}|R{0.086\linewidth}|L{0.190\linewidth}|L{0.190\linewidth}|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endfirsthead
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
GO & A & Jerami Grant OVER 2.5 assists @ +140 (fanduel) & 53.6\% & Strong edge (+28.7\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.287). \\
\hline
\end{longtable}
}


\newpage

\subsubsection*{DAL @ LAL}
\begin{itemize}
\item Tip (ET): \texttt{10:10 PM ET}
\item Listed plays: \texttt{5}
\end{itemize}

{\small
\setlength{\tabcolsep}{2pt}
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\begin{longtable}{|L{0.112\linewidth}|L{0.112\linewidth}|L{0.190\linewidth}|R{0.086\linewidth}|L{0.190\linewidth}|L{0.190\linewidth}|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endfirsthead
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
GO & A & LeBron James OVER 40.5 points+rebounds+assists @ -106 (fanduel) & 68.4\% & Strong edge (+33.0\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.330). \\
\hline
GO & A & Austin Reaves OVER 36.5 points+rebounds+assists @ -106 (fanduel) & 68.1\% & Strong edge (+32.4\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.324). \\
\hline
GO & A & Marcus Smart OVER 18.5 points+rebounds+assists @ -102 (fanduel) & 66.0\% & Strong edge (+30.7\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.307). \\
\hline
GO & B & Jake LaRavia OVER 16.5 points+rebounds+assists @ -102 (draftkings) & 65.8\% & Strong edge (+30.3\% est.), Higher stake & Go: verified availability with tier B market depth and positive edge (EV 0.303). \\
\hline
GO & A & LeBron James OVER 8.5 assists @ +112 (fanduel) & 61.4\% & Strong edge (+30.1\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.301). \\
\hline
\end{longtable}
}


\newpage

\subsection*{Data Quality}

\begin{itemize}
\item Model uses market-implied fair probabilities with injury/roster/opponent adjustments.
\item Minutes/usage projection uses deterministic v0 rules, not learned distributions.
\item SGP/SGPx correlation uses deterministic haircut rules (v0).
\item \texttt{unknown\_roster} means the roster feed did not return a trusted active/inactive record for that player in that game snapshot.
\item \texttt{unknown\_event} means event-to-team mapping was missing, so player-to-game roster checks could not be resolved.
\end{itemize}

\subsection*{Confidence}

\begin{itemize}
\item Recommendations reflect the model probabilities and EVs supplied in the payload; do not assume any data beyond this JSON.
\item NO-GO items were marked in the payload primarily due to low EV and questionable injury status; consult live injury/in-play feeds before any action.
\end{itemize}

\subsubsection*{Interpreting p(hit)}

\begin{itemize}
\item \texttt{p(hit)} = estimated chance the recommended side wins at that line.
\item Built from no-vig odds + small injury/roster/spread adjustments (clamped 1\%-99\%).
\item Use it to rank EV, not as a guarantee; judge it by calibration over many bets.
\item Can be wrong when odds are stale, coverage is thin, or minutes/role are uncertain.
\end{itemize}
\end{document}
