\documentclass[10pt]{article}
\usepackage[margin=1in,landscape]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{array}
\usepackage{ragged2e}
\newcolumntype{L}[1]{>{\RaggedRight\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\RaggedLeft\arraybackslash}p{#1}}
\renewcommand{\arraystretch}{1.05}
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}
\sloppy
\begin{document}
\begin{center}\LARGE\textbf{NBA Strategy Brief (DraftKings)}\end{center}
\vspace{0.5em}
\section*{Strategy Brief (DraftKings Execution Only)}

\subsection*{Snapshot}
\begin{itemize}
\item snapshot\_id: \texttt{daily-20260212T230052Z}
\item modeled\_date\_et: \texttt{Thursday, Feb 12, 2026 (ET)}
\item generated\_at\_et: \texttt{2026-02-12 06:52:00 PM EST}
\item source\_data: \texttt{snapshot\_inputs}
\item scoring: \texttt{deterministic}
\item narrative: \texttt{deterministic\_fallback}
\item llm\_pass1\_status: \texttt{fallback}
\item llm\_pass2\_status: \texttt{fallback}
\end{itemize}

\subsection*{What The Bet Is}

\begin{itemize}
\item Bet type: single-player props (over/under stat lines).
\item Not a game-winner (moneyline) strategy.
\item Injury and roster checks are used as action gates.
\item Tier A = 2+ book quotes for a line; Tier B = a single-book quote.
\end{itemize}

\subsection*{Executive Summary}

\begin{itemize}
\item 3 games, 190 candidate lines, 50 eligible plays after gates.
\item Eligible plays: \texttt{50} out of \texttt{190} candidate lines.
\item Tier-B mode: \texttt{enabled}. Candidate mix: Tier A \texttt{110}, Tier B \texttt{80}.
\item Gated-out lines hidden from this brief: \texttt{0}.
\item First-page table below shows the top \texttt{5} plays across all games.
\end{itemize}

\subsection*{Action Plan (GO / LEAN / NO-GO)}

\subsubsection*{Top 5 Across All Games}

{\small
\setlength{\tabcolsep}{2pt}
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\begin{longtable}{|L{0.089\linewidth}|L{0.164\linewidth}|L{0.089\linewidth}|L{0.150\linewidth}|R{0.068\linewidth}|L{0.150\linewidth}|L{0.150\linewidth}|}
\hline
\textbf{Action} & \textbf{Game} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endfirsthead
\hline
\textbf{Action} & \textbf{Game} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
GO & DAL @ LAL & B & Jake LaRavia OVER 16.5 points+rebounds+assists @ -102 (draftkings) & 65.8\% & Strong edge (+30.3\% est.), Higher stake & Go: verified availability with tier B market depth and positive edge (EV 0.303). (tier=B; injury=available\_unlisted; roster=active) \\
\hline
GO & DAL @ LAL & A & Marcus Smart OVER 18.5 points+rebounds+assists @ -104 (draftkings) & 66.0\% & Strong edge (+29.4\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.294). (tier=A; injury=available\_unlisted; roster=active) \\
\hline
GO & DAL @ LAL & A & Brandon Williams OVER 22.5 points+rebounds+assists @ -107 (draftkings) & 66.8\% & Strong edge (+29.3\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.293). (tier=A; injury=available\_unlisted; roster=active) \\
\hline
GO & DAL @ LAL & A & Marcus Smart OVER 11.5 points @ -101 (draftkings) & 64.5\% & Strong edge (+28.4\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.284). (tier=A; injury=available\_unlisted; roster=active) \\
\hline
GO & MIL @ OKC & A & Kevin Porter Jr. OVER 31.5 points+rebounds+assists @ -107 (draftkings) & 66.3\% & Strong edge (+28.4\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.284). (tier=A; injury=available\_unlisted; roster=active) \\
\hline
\end{longtable}
}




\newpage

\subsection*{Game Cards by Matchup}

\subsubsection*{MIL @ OKC}
\begin{itemize}
\item Tip (ET): \texttt{07:40 PM ET}
\item Listed plays: \texttt{5}
\end{itemize}

{\small
\setlength{\tabcolsep}{2pt}
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\begin{longtable}{|L{0.112\linewidth}|L{0.112\linewidth}|L{0.190\linewidth}|R{0.086\linewidth}|L{0.190\linewidth}|L{0.190\linewidth}|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endfirsthead
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
GO & A & Kevin Porter Jr. OVER 31.5 points+rebounds+assists @ -107 (draftkings) & 66.3\% & Strong edge (+28.4\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.284). \\
\hline
GO & A & Jericho Sims OVER 5.5 points @ +100 (draftkings) & 63.6\% & Strong edge (+27.3\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.273). \\
\hline
GO & A & A.J. Green OVER 15.5 points+rebounds+assists @ -113 (draftkings) & 67.4\% & Strong edge (+27.1\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.271). \\
\hline
GO & A & Chet Holmgren OVER 30.5 points+rebounds+assists @ -112 (draftkings) & 66.2\% & Strong edge (+25.2\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.252). \\
\hline
GO & B & Myles Turner OVER 13.5 points @ -104 (draftkings) & 63.8\% & Strong edge (+25.2\% est.), Higher stake & Go: verified availability with tier B market depth and positive edge (EV 0.252). \\
\hline
\end{longtable}
}


\newpage

\subsubsection*{POR @ UTA}
\begin{itemize}
\item Tip (ET): \texttt{09:10 PM ET}
\item Listed plays: \texttt{5}
\end{itemize}

{\small
\setlength{\tabcolsep}{2pt}
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\begin{longtable}{|L{0.112\linewidth}|L{0.112\linewidth}|L{0.190\linewidth}|R{0.086\linewidth}|L{0.190\linewidth}|L{0.190\linewidth}|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endfirsthead
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
GO & A & Donovan Clingan OVER 1.5 three-pointers @ +171 (draftkings) & 46.7\% & Strong edge (+26.5\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.265). \\
\hline
GO & A & Jrue Holiday OVER 26.5 points+rebounds+assists @ -104 (draftkings) & 63.3\% & Strong edge (+24.2\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.242). \\
\hline
GO & A & Jrue Holiday OVER 2.5 three-pointers @ +145 (draftkings) & 50.6\% & Strong edge (+23.9\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.239). \\
\hline
GO & A & Jerami Grant OVER 25.5 points+rebounds+assists @ -116 (draftkings) & 66.5\% & Strong edge (+23.8\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.238). \\
\hline
GO & B & Toumani Camara OVER 14.5 points @ +101 (draftkings) & 61.1\% & Strong edge (+22.8\% est.), Higher stake & Go: verified availability with tier B market depth and positive edge (EV 0.228). \\
\hline
\end{longtable}
}


\newpage

\subsubsection*{DAL @ LAL}
\begin{itemize}
\item Tip (ET): \texttt{10:10 PM ET}
\item Listed plays: \texttt{5}
\end{itemize}

{\small
\setlength{\tabcolsep}{2pt}
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\begin{longtable}{|L{0.112\linewidth}|L{0.112\linewidth}|L{0.190\linewidth}|R{0.086\linewidth}|L{0.190\linewidth}|L{0.190\linewidth}|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endfirsthead
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{p(hit)} & \textbf{Edge Note} & \textbf{Why} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
GO & B & Jake LaRavia OVER 16.5 points+rebounds+assists @ -102 (draftkings) & 65.8\% & Strong edge (+30.3\% est.), Higher stake & Go: verified availability with tier B market depth and positive edge (EV 0.303). \\
\hline
GO & A & Marcus Smart OVER 18.5 points+rebounds+assists @ -104 (draftkings) & 66.0\% & Strong edge (+29.4\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.294). \\
\hline
GO & A & Brandon Williams OVER 22.5 points+rebounds+assists @ -107 (draftkings) & 66.8\% & Strong edge (+29.3\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.293). \\
\hline
GO & A & Marcus Smart OVER 11.5 points @ -101 (draftkings) & 64.5\% & Strong edge (+28.4\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.284). \\
\hline
GO & A & Jake LaRavia OVER 1.5 three-pointers @ +137 (draftkings) & 54.1\% & Strong edge (+28.2\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.282). \\
\hline
\end{longtable}
}


\newpage

\subsection*{Data Quality}

\begin{itemize}
\item Execution report: all tickets priced and executed on DraftKings only.
\item Actionable rows require DraftKings price >= PLAY-TO for the chosen side.
\item Model uses market-implied fair probabilities with injury/roster/opponent adjustments.
\item Minutes/usage projection uses deterministic v0 rules, not learned distributions.
\item SGP/SGPx correlation uses deterministic haircut rules (v0).
\item \texttt{unknown\_roster} means the roster feed did not return a trusted active/inactive record for that player in that game snapshot.
\item \texttt{unknown\_event} means event-to-team mapping was missing, so player-to-game roster checks could not be resolved.
\end{itemize}

\subsection*{Confidence}

\begin{itemize}
\item Tier A lines are preferred over Tier B by default.
\item Model probabilities are market-implied with injury/roster adjustments.
\end{itemize}

\subsubsection*{Interpreting p(hit)}

\begin{itemize}
\item \texttt{p(hit)} = estimated chance the recommended side wins at that line.
\item Built from no-vig odds + small injury/roster/spread adjustments (clamped 1\%-99\%).
\item Use it to rank EV, not as a guarantee; judge it by calibration over many bets.
\item Can be wrong when odds are stale, coverage is thin, or minutes/role are uncertain.
\end{itemize}
\end{document}
