\documentclass[10pt]{article}
\usepackage[margin=1in,landscape]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{ragged2e}
\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}
\renewcommand{\arraystretch}{1.05}
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}
\sloppy
\begin{document}
\begin{center}\LARGE\textbf{NBA Strategy Brief}\end{center}
\vspace{0.5em}
\subsection*{Snapshot}
\begin{itemize}
\item source\_data: \texttt{snapshot\_inputs}
\item scoring: \texttt{deterministic}
\item narrative: \texttt{llm}
\item llm\_pass1\_status: \texttt{fallback}
\end{itemize}
Date: generated 2026-02-11 UTC snapshot\_id daily-20260211T230026Z.
Slate summary: 8 games, 497 candidate lines, 329 eligible plays after gates. This brief covers player-prop over/under bets only (not game-winner or spread bets). Many plays show model edge but carry roster/injury uncertainty.

\subsection*{What The Bet Is}
Player-prop over/under wagers — single-player totals (points, threes, rebounds, assists, or combined PRA). Each recommended ticket below is the specific market (e.g., "Player OVER X") and the listed book/price.

\subsection*{Executive Summary}
\begin{itemize}
\item No clear GOs — model shows many positive-expected-value plays but the decision gate defaults to LEAN because injury or roster signals are not clean.
\item Highest-priority opportunities (by modeled EV) are Jay Huff OVER 13.5 (IND @ BKN) and several Kam Jones lines (IND @ BKN), plus Jarrett Allen OVER 28.5 PRA (WAS @ CLE). All are LEAN recommendations due to uncertainty.
\item Several tickets are explicitly NO-GO because of roster/injury gates (players not on roster or confirmed out); do not bet those.
\item Data gaps: minutes/usage and correlation rules are deterministic (v0), not learned from distributions — treat projected usage as less robust.
\end{itemize}


\newpage

\subsection*{Analyst Take}

\begin{itemize}
\item mode: \texttt{llm\_web}
\end{itemize}

\subsubsection*{Read This First}

The model produced a slate-level summary and top plays for an 8-game slate with 329 eligible lines. Top recommended 'LEAN' plays concentrate on IND @ BKN props (Jay Huff and Kam Jones) and a WAS @ CLE prop (Jarrett Allen).

\subsubsection*{News Signals}

\begin{itemize}
\item Refutes/Risks:
\item [S1] Recent game recaps and box scores show Jarrett Allen logged a 22/13 double-double in a Cavaliers game, which is lower than the model's suggested OVER 28.5 points+rebounds+assists ticket.
\item [S2] Jay Huff has recorded a career-high 29 points in at least one recent Pacers game, indicating volatility around his point totals relative to the model's Jay Huff OVER 13.5 points play.
\end{itemize}

\subsubsection*{Bottom Line}

\begin{itemize}
\item \textbf{Best Bet:} \textbf{Jay Huff OVER 13.5 points @ +102 (fanduel)}
\item \textbf{Lookup Line:} \texttt{IND @ BKN} | \texttt{OVER 13.5 points} | \texttt{fanduel +102}
\end{itemize}
The deterministic model offers specific actionable 'LEAN' prop recommendations and clearly states its methodological limits (deterministic minutes/usage and correlation rules). External box-score evidence partially challenges the Allen OVER 28.5 PRA ticket (recent 22/13) while showing Huff has upside (career-high 29) but also variability.

\subsubsection*{Source Index}

\begin{itemize}
\item [S1] CBSSports recap: Cavaliers Jarrett Allen double-double (www.cbssports.com)
\item [S2] CBSSports: Pacers Jay Huff nets career-high 29 points (www.cbssports.com)
\item Deterministic model details are summarized in Snapshot/Action Plan.
\item Full source URLs are stored in \texttt{brief-analyst.json} for audit/debug use.
\end{itemize}

\newpage

\subsection*{Best Available Bet Right Now}

\begin{itemize}
\item \textbf{Decision:} \textbf{LEAN} (no GO passed clean gates in this snapshot; this is the highest-ranked LEAN.)
\item \textbf{Bet:} \textbf{Jay Huff OVER 13.5 points @ +102 (fanduel)}
\item \textbf{Lookup Line:} \texttt{IND @ BKN} | \texttt{OVER 13.5 points} | \texttt{fanduel +102}
\item \textbf{Model Edge:} \texttt{+24.0\% est.}
\item why: Lean only: edge exists (EV 0.240) with non-clean injury status.
\end{itemize}

\newpage

\subsection*{Action Plan (GO / LEAN / NO-GO)}

\subsubsection*{Top 5 Across All Games}

This is player-prop over/under betting, not game winner bets.

\begin{tabularx}{\textwidth}{|l|Y|l|Y|Y|Y|}
\hline
\textbf{Action} & \textbf{Game} & \textbf{Tier} & \textbf{Ticket} & \textbf{Edge Note} & \textbf{Why} \\
\hline
LEAN & IND @ BKN & A & Jay Huff OVER 13.5 points @ +102 (fanduel) & Strong edge (+24.0\% est.) & High EV but injury/availability flagged non-clean — size down. \\
\hline
LEAN & IND @ BKN & B & Kam Jones OVER 22.5 points+rebounds+assists @ -113 (fanduel) & Strong edge (+21.8\% est.) & Good EV; roster/injury status uncertain — prefer smaller stake. \\
\hline
LEAN & IND @ BKN & A & Kam Jones OVER 1.5 three-pointers @ +130 (draftkings) & Strong edge (+21.1\% est.) & Positive EV; same availability caveat. \\
\hline
LEAN & WAS @ CLE & A & Jarrett Allen OVER 28.5 points+rebounds+assists @ -104 (fanduel) & Strong edge (+21.0\% est.) & High modeled probability but injury/role not fully clean. \\
\hline
LEAN & IND @ BKN & B & Kam Jones OVER 13.5 points @ -104 (fanduel) & Strong edge (+20.9\% est.) & Similar reasons — lean only. \\
\hline
NO-GO & WAS @ CLE & B & Carlton Carrington UNDER 2.5 rebounds @ +124 (draftkings) & Watch: roster\_gate & Player not confirmed on roster — do not bet. \\
\hline
NO-GO & LAC @ HOU & B & Derrick Jones UNDER 2.5 rebounds @ +123 (draftkings) & Watch: roster\_gate & Roster check failed — no bet. \\
\hline
NO-GO & IND @ BKN & A & Jarace Walker UNDER 5.5 rebounds @ +111 (draftkings) & Watch: injury\_gate & Player injury risk too high — no bet. \\
\hline
\end{tabularx}


Order: GO first (none), then LEAN, then NO-GO. If roster or injury status clears positively pregame and you accept model assumptions, consider moving LEANs toward small bets.



\newpage

\subsection*{Game Cards by Matchup}

\subsubsection*{WAS @ CLE}
\begin{itemize}
\item Tip (ET): \texttt{07:10 PM ET}
\item Listed plays: \texttt{5}
\end{itemize}

\begin{tabularx}{\textwidth}{|l|l|Y|Y|Y|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{Edge Note} & \textbf{Why} \\
\hline
LEAN & A & Jarrett Allen OVER 28.5 points+rebounds+assists @ -104 (fanduel) & Strong edge (+21.0\% est.), Higher stake & Lean only: edge exists (EV 0.210) with non-clean injury status. \\
\hline
LEAN & A & Tre Johnson OVER 14.5 points @ -102 (fanduel) & Strong edge (+19.0\% est.), Higher stake & Lean only: edge exists (EV 0.190) with non-clean injury status. \\
\hline
LEAN & A & Donovan Mitchell OVER 3.5 three-pointers @ +130 (fanduel) & Strong edge (+18.9\% est.), Higher stake & Lean only: edge exists (EV 0.189) with non-clean injury status. \\
\hline
LEAN & A & Alex Sarr OVER 26.5 points+rebounds+assists @ -105 (draftkings) & Strong edge (+18.8\% est.), Higher stake & Lean only: edge exists (EV 0.188) with non-clean injury status. \\
\hline
LEAN & A & Jaylon Tyson OVER 13.5 points @ +102 (fanduel) & Strong edge (+18.7\% est.), Higher stake & Lean only: edge exists (EV 0.187) with non-clean injury status. \\
\hline
\end{tabularx}


\newpage

\subsubsection*{NYK @ PHI}
\begin{itemize}
\item Tip (ET): \texttt{07:30 PM ET}
\item Listed plays: \texttt{1}
\end{itemize}

\begin{tabularx}{\textwidth}{|l|l|Y|Y|Y|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{Edge Note} & \textbf{Why} \\
\hline
LEAN & A & Landry Shamet OVER 2.5 three-pointers @ +124 (fanduel) & Strong edge (+18.2\% est.), Higher stake & Lean only: edge exists (EV 0.182) with non-clean injury status. \\
\hline
\end{tabularx}


\newpage

\subsubsection*{IND @ BKN}
\begin{itemize}
\item Tip (ET): \texttt{07:40 PM ET}
\item Listed plays: \texttt{5}
\end{itemize}

\begin{tabularx}{\textwidth}{|l|l|Y|Y|Y|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{Edge Note} & \textbf{Why} \\
\hline
LEAN & A & Jay Huff OVER 13.5 points @ +102 (fanduel) & Strong edge (+24.0\% est.), Higher stake & Lean only: edge exists (EV 0.240) with non-clean injury status. \\
\hline
LEAN & B & Kam Jones OVER 22.5 points+rebounds+assists @ -113 (fanduel) & Strong edge (+21.8\% est.), Higher stake & Lean only: edge exists (EV 0.218) with non-clean injury status. \\
\hline
LEAN & A & Kam Jones OVER 1.5 three-pointers @ +130 (draftkings) & Strong edge (+21.1\% est.), Higher stake & Lean only: edge exists (EV 0.211) with non-clean injury status. \\
\hline
LEAN & B & Kam Jones OVER 13.5 points @ -104 (fanduel) & Strong edge (+20.9\% est.), Higher stake & Lean only: edge exists (EV 0.209) with non-clean injury status. \\
\hline
LEAN & B & Kam Jones OVER 21.5 points+rebounds+assists @ -121 (draftkings) & Strong edge (+20.2\% est.), Higher stake & Lean only: edge exists (EV 0.202) with non-clean injury status. \\
\hline
\end{tabularx}


\newpage

\subsection*{Data Quality}
Known limitations (plain):
\begin{itemize}
\item Minutes/usage projections use deterministic rules (v0), not probabilistic distributions — projections can be brittle, especially on role changes.
\item Correlation rules for multi-leg/SGP exposure use deterministic haircuts (v0).
\item Model probabilities are market-implied with adjustments for injury/roster/opponent, but many lines still show "unknown" injury status. Data is therefore mixed quality for late-breaking availability. If roster/injury info is missing or weak, that increases risk.
\end{itemize}

\subsection*{Confidence}
Overall confidence: Moderate for direction (model consistently finds overs) but Low-to-Moderate for execution because of roster/injury uncertainty and deterministic usage assumptions. Tier A lines preferred over Tier B when sizing. If you act, use reduced stake sizes on LEAN plays and avoid NO-GO tickets.
\end{document}
