\documentclass[10pt]{article}
\usepackage[margin=1in,landscape]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{ragged2e}
\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}
\renewcommand{\arraystretch}{1.05}
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}
\sloppy
\begin{document}
\begin{center}\LARGE\textbf{NBA Strategy Brief}\end{center}
\vspace{0.5em}
\subsection*{Snapshot}
\begin{itemize}
\item source\_data: \texttt{snapshot\_inputs}
\item scoring: \texttt{deterministic}
\item narrative: \texttt{llm}
\end{itemize}
Date: 2026-02-12 (generated 00:28:45Z).
Scope: Player-prop over/under bets for tonight's slate. Top plays span IND@BKN, NYK@PHI, ATL@CHA, WAS@CLE. All recommended plays below are player-prop over/under markets (not game-winner bets). Data comes solely from the provided strategy payload; confirm live odds and availability before wagering.

\subsection*{What The Bet Is}
Player-prop over/under bets (examples: points, assists, points+rebounds+assists, three-pointers). Recommendations are model-backed "over" plays where the model estimates a positive expected value versus the posted market. These are not side/point-spread or game outcome wagers.

\subsection*{Executive Summary}
\begin{itemize}
\item Multiple Tier A player-prop overs show strong model edges and available roster status. Top, highest-confidence plays include Day'Ron Sharpe O 14.5 (DK), Nolan Traore O 5.5 assists (FD), Drake Powell O 11.5 PRA (DK), Kelly Oubre Jr O 24.5 PRA (DK), and Onyeka Okongwu O 24.5 PRA (FD).
\item Several other Tier A/B overs are listed as additional GO opportunities. Watchlist contains NO-GO items where roster/injury gates prevent wagering.
\item Important: this brief relies solely on the supplied JSON. If any "available\_unlisted", "unknown", or "out" values exist for a player, confirm final availability and current odds before placing bets.
\end{itemize}


\newpage

\subsection*{Analyst Take}

\begin{itemize}
\item mode: \texttt{llm\_web}
\end{itemize}

\subsubsection*{Read This First}

The provided deterministic model identifies five Tier A "GO" player-prop plays across three NBA games, led by Day'Ron Sharpe (IND @ BKN) and Nolan Traore (IND @ BKN). The model uses market-implied probabilities with manual adjustments for injuries/rosters/opponents and applies deterministic (v0) rules for minutes/usage projections and correlation haircuts.

\subsubsection*{News Signals}

\begin{itemize}
\item Supports:
\item [S1] Day'Ron Sharpe has been highlighted by game coverage and box-score reporting as an active contributor in Nets games, consistent with a model selecting him as a top prop play.
\item [S2] Kelly Oubre Jr. has a recent official injury designation from the NBA (knee) that could affect his availability and thus the model's adjustments for player usage and prop evaluations.
\item [S3] Onyeka Okongwu has recorded a recent double-double (15 points, 10 rebounds) in game action, supporting model selection of him as a Tier A prop candidate for points+rebounds+assists markets.
\item Refutes/Risks:
\item [S4] Public game previews and reporting do not provide independent market EV calculations; available news sources do not confirm the model's stated edge magnitudes for the listed top\_plays.
\end{itemize}

\subsubsection*{Bottom Line}

\begin{itemize}
\item \textbf{Best Bet:} \textbf{Day'Ron Sharpe OVER 14.5 points @ -103 (draftkings)}
\item \textbf{Lookup Line:} \texttt{IND @ BKN} | \texttt{OVER 14.5 points} | \texttt{draftkings -103}
\end{itemize}
The model surfaces several plausible Tier A player-prop candidates and incorporates roster/injury adjustments; independent news sources provide some supporting performance and injury context (e.g., Sharpe, Okongwu, Oubre). However, the model relies on deterministic v0 rules for minutes/usage and correlation haircuts rather than learned distributions, and external sources do not corroborate the specific EV values.

\subsubsection*{Source Index}

\begin{itemize}
\item [S1] Nets vs Wizards 127-113 (game coverage mentioning Day'Ron Sharpe) (www.netsdaily.com)
\item [S2] 76ers: Kelly Oubre Jr. out with knee injury; will be reevaluated in two weeks (www.nba.com)
\item [S3] Onyeka Okongwu posts double-double with 15 points and 10 rebounds as Hawks defeat Hornets (www.fanduel.com)
\item [S4] Knicks at 76ers game preview (news coverage lacks market EV details) (www.postingandtoasting.com)
\item Deterministic model details are summarized in Snapshot/Action Plan.
\item Full source URLs are stored in \texttt{brief-analyst.json} for audit/debug use.
\end{itemize}

\newpage

\subsection*{Best Available Bet Right Now}

\begin{itemize}
\item \textbf{Decision:} \textbf{GO} (meets clean GO gates in this snapshot.)
\item \textbf{Bet:} \textbf{Day'Ron Sharpe OVER 14.5 points @ -103 (draftkings)}
\item \textbf{Lookup Line:} \texttt{IND @ BKN} | \texttt{OVER 14.5 points} | \texttt{draftkings -103}
\item \textbf{Model Edge:} \texttt{+35.2\% est.}
\item why: Go: verified availability with tier A market depth and positive edge (EV 0.352).
\end{itemize}

\newpage

\subsection*{Action Plan (GO / LEAN / NO-GO)}

\subsubsection*{Top 5 Across All Games}

Note: This is player-prop over/under betting, not game winner bets.

\begin{tabularx}{\textwidth}{|l|Y|l|Y|Y|Y|}
\hline
\textbf{Action} & \textbf{Game} & \textbf{Tier} & \textbf{Ticket} & \textbf{Edge Note} & \textbf{Why} \\
\hline
GO & IND @ BKN & A & Day'Ron Sharpe OVER 14.5 points @ -103 (draftkings) & Strong edge (+35.2\% est.), Higher stake & Model shows substantial positive EV and player is listed active with Tier A market depth. \\
\hline
GO & IND @ BKN & A & Nolan Traore OVER 5.5 assists @ +130 (fanduel) & Strong edge (+34.3\% est.), Higher stake & Positive edge with Tier A depth; assists over at a plus price. \\
\hline
GO & IND @ BKN & A & Drake Powell OVER 11.5 points+rebounds+assists @ +101 (draftkings) & Strong edge (+34.2\% est.), Higher stake & Combined PRA line shows meaningful edge and active roster status. \\
\hline
GO & NYK @ PHI & A & Kelly Oubre Jr OVER 24.5 points+rebounds+assists @ -104 (draftkings) & Strong edge (+33.8\% est.), Higher stake & Model probability and Tier A depth indicate a positive edge; availability confirmed. \\
\hline
GO & ATL @ CHA & A & Onyeka Okongwu OVER 24.5 points+rebounds+assists @ -102 (fanduel) & Strong edge (+33.8\% est.), Higher stake & Tier A market depth and model edge; player listed available. \\
\hline
LEAN & IND @ BKN & A & Jay Huff OVER 13.5 points @ +102 (fanduel) & Strong edge (+33.6\% est.) & Good EV but lower event prominence vs top GO picks—consider smaller stake or diversify. \\
\hline
LEAN & NYK @ PHI & B & Dominick Barlow OVER 14.5 PRA @ -104 (draftkings) & Strong edge (+31.6\% est.) & Tier B depth; acceptable but allocate smaller unit size. \\
\hline
NO-GO & WAS @ CLE & B & Carlton Carrington UNDER 2.5 rebounds @ +124 (draftkings) & Roster/injury uncertainty & Roster check did not confirm active status; pre-bet readiness false—do not bet. \\
\hline
NO-GO & LAC @ HOU & B & Derrick Jones UNDER 2.5 rebounds @ +123 (draftkings) & Roster/injury uncertainty & Roster/injury gate flagged; pre-bet readiness false—do not bet. \\
\hline
NO-GO & WAS @ CLE & B & Alex Sarr UNDER 0.5 three-pointers @ +151 (draftkings) & Player listed out & High availability risk (injury status = out). \\
\hline
\end{tabularx}




\newpage

\subsection*{Game Cards by Matchup}

\subsubsection*{ATL @ CHA}
\begin{itemize}
\item Tip (ET): \texttt{07:10 PM ET}
\item Listed plays: \texttt{2}
\end{itemize}

\begin{tabularx}{\textwidth}{|l|l|Y|Y|Y|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{Edge Note} & \textbf{Why} \\
\hline
GO & A & Onyeka Okongwu OVER 24.5 points+rebounds+assists @ -102 (fanduel) & Strong edge (+33.8\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.338). \\
\hline
GO & A & Zaccharie Risacher OVER 1.5 three-pointers @ +162 (fanduel) & Strong edge (+32.3\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.323). \\
\hline
\end{tabularx}


\newpage

\subsubsection*{WAS @ CLE}
\begin{itemize}
\item Tip (ET): \texttt{07:10 PM ET}
\item Listed plays: \texttt{1}
\end{itemize}

\begin{tabularx}{\textwidth}{|l|l|Y|Y|Y|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{Edge Note} & \textbf{Why} \\
\hline
GO & A & Jarrett Allen OVER 28.5 points+rebounds+assists @ -104 (fanduel) & Strong edge (+31.1\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.311). \\
\hline
\end{tabularx}


\newpage

\subsubsection*{NYK @ PHI}
\begin{itemize}
\item Tip (ET): \texttt{07:30 PM ET}
\item Listed plays: \texttt{5}
\end{itemize}

\begin{tabularx}{\textwidth}{|l|l|Y|Y|Y|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{Edge Note} & \textbf{Why} \\
\hline
GO & A & Kelly Oubre Jr OVER 24.5 points+rebounds+assists @ -104 (draftkings) & Strong edge (+33.8\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.338). \\
\hline
GO & B & Dominick Barlow OVER 14.5 points+rebounds+assists @ -104 (draftkings) & Strong edge (+31.6\% est.), Higher stake & Go: verified availability with tier B market depth and positive edge (EV 0.316). \\
\hline
GO & B & Dominick Barlow OVER 8.5 points @ +107 (draftkings) & Strong edge (+31.4\% est.), Higher stake & Go: verified availability with tier B market depth and positive edge (EV 0.314). \\
\hline
GO & B & Kelly Oubre Jr OVER 2.5 three-pointers @ +148 (fanduel) & Strong edge (+31.2\% est.), Higher stake & Go: verified availability with tier B market depth and positive edge (EV 0.312). \\
\hline
GO & B & VJ Edgecombe OVER 24.5 points+rebounds+assists @ -108 (draftkings) & Strong edge (+31.1\% est.), Higher stake & Go: verified availability with tier B market depth and positive edge (EV 0.311). \\
\hline
\end{tabularx}


\newpage

\subsubsection*{IND @ BKN}
\begin{itemize}
\item Tip (ET): \texttt{07:40 PM ET}
\item Listed plays: \texttt{5}
\end{itemize}

\begin{tabularx}{\textwidth}{|l|l|Y|Y|Y|}
\hline
\textbf{Action} & \textbf{Tier} & \textbf{Ticket} & \textbf{Edge Note} & \textbf{Why} \\
\hline
GO & A & Day'Ron Sharpe OVER 14.5 points @ -103 (draftkings) & Strong edge (+35.2\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.352). \\
\hline
GO & A & Nolan Traore OVER 5.5 assists @ +130 (fanduel) & Strong edge (+34.3\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.343). \\
\hline
GO & A & Drake Powell OVER 11.5 points+rebounds+assists @ +101 (draftkings) & Strong edge (+34.2\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.342). \\
\hline
GO & A & Danny Wolf OVER 14.5 points @ +100 (fanduel) & Strong edge (+33.7\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.337). \\
\hline
GO & A & Jay Huff OVER 13.5 points @ +102 (fanduel) & Strong edge (+33.6\% est.), Higher stake & Go: verified availability with tier A market depth and positive edge (EV 0.336). \\
\hline
\end{tabularx}


\newpage

\subsection*{Data Quality}
\begin{itemize}
\item Source: All information is taken exactly from the provided JSON. No external verification or live odds refresh performed.
\item Known gaps from payload: model uses deterministic minutes/usage rules (not learned distributions); SGP/SGPx correlation uses deterministic haircut rules (v0). These can understate actual variance in lineups and correlations.
\item Roster/injury fields include values like "available\_unlisted", "unknown", and "out". When non-"available" values appear, reliability drops and bets should be confirmed manually.
\end{itemize}

\subsection*{Confidence}
\begin{itemize}
\item Overall confidence in listed GO plays: medium-high for Tier A items where roster status = active/
\end{itemize}
\end{document}
